% chapters/04_injection.tex

\chapter{Script Injection}
\epigraph{``I can see clearly now, the rain is gone.\\I can see all obstacles in my way.''}{Johnny Nash, “I Can See Clearly Now”}

The transition did not happen in a lab. There were no gleaming chrome chairs or neural jacks. Instead, Kael led her to a small alcove in the back of the warehouse, where a young man—Jax—was hunched over a desk made of reclaimed cedar and matte-black hardware. 

Jax didn't look up. His fingers danced across a keyboard that didn't click; it whispered. 

``She's a Junior Logistics Analyst,'' Kael said, his voice echoing slightly in the small space. ``Standard Aegis-7 firmware. High-tier encryption, low-tier agency.''

Jax stopped. He looked at Elara, his eyes tracking the subtle, rhythmic flicker of her iris—the tell-tale sign of the corporate HUD trying to re-establish a handshake with the city grid. ``The Aegis doesn't just show you the world, Elara. It filters the world. It’s a firewall between your intent and your reality.''

Elara felt a spike of defensive instinct—the ghost of a corporate training module she’d attended in her first week. ``It’s for my safety. It manages my health metrics. It optimizes my route.''

``It optimizes your exhaustion,'' Jax countered, his voice flat but not unkind. He held up a small, translucent chip. ``This isn't a virus. It’s a translator. It doesn't break the Aegis; it just tells it to stop lying to you.''

He leaned forward, gesturing for her to sit. ``This will feel like a migraine for about three seconds. Then, it will feel like waking up.''



Jax didn't touch her eye. He simply placed the chip against the side of her temple, near the Aegis-7’s external induction port. 

The world shattered.

First came the white noise—a high-pitched shriek that felt like a needle being driven through her eardrum. Then, the blue neon of the Legacy HUD began to melt. The words `RESTRICTED', `DEBT', and `PENDING' dissolved into liquid light, running down the inside of her vision like rain on a windshield. 

Elara gasped, her hands gripping the edges of the cedar desk. ``I can't... I can't see.''

``Don't look with the eye,'' Jax’s voice sounded miles away. ``Look with the protocol.''

Then, the static cleared. 

The grey Fog of Seattle didn't disappear—it was still raining, and the world was still charcoal and shadow—but the \textbf{Signal} had changed. 

The Aegis-7 was still functioning, but it was no longer reporting to the Auditor. The HUD was now a deep, bioluminescent green. As she looked toward the warehouse wall, she didn't see `ASSET ID: NULL`. She saw a shimmering, geometric lattice.

\systemcall{NODE: NOURISHMENT-01 // STATUS: METABOLIC EQUILIBRIUM \\ UTILITY: 94\% // CURRENT DEMAND: 12 UNITS (LOW) \\ DESIGNER: UNASSIGNED}

She turned her head toward the street outside the warehouse. Through the steel door, the lens filtered the city in a way that made her breath hitch. The apartment complex across the street, usually a black box of `RESIDENTIAL TIER 5', was now a heatmap of \textbf{Unmet Demand}.

Small, pulsing golden icons hovered over the windows. 
\textit{Need: Clean Water (Filter Failure).}
\textit{Need: Thermal Regulation (Window Breach).}
\textit{Need: Skill Verification (Logistics).}

``What am I seeing?'' she whispered, her voice trembling. 

``You’re seeing the truth of the city,'' Kael said, standing behind her. ``The Legacy market sees those people as `Delinquent Accounts.' But the Mesh sees them as `Opportunities for Utility.' You’re no longer looking at a map of who can pay, Elara. You’re looking at a map of what needs to be done.''



Elara stood up, her legs feeling strangely light. She looked at Jax. ``The Aegis... it’s not reporting my location anymore?''

Jax finally offered a small, crooked smile. ``As far as the Auditor is concerned, you’re currently a `Telemetry Fault' in a dead zone. You’ve been de-listed. You’re a ghost in their machine, and a Designer in ours.''

Elara walked to the window and pressed her hand against the glass. The golden icons of the neighbors' needs pulsed in time with her own heartbeat. For years, she had felt like a victim of the city’s inefficiency. Now, for the first time, she felt like the solution.

She looked at Kael. ``Show me how to answer the call.''
