% chapters/07_discrepancy.tex

\chapter{The Discrepancy}
\epigraph{``Control is a pursuit, not a destination.''}{Attributed to various Cybernetics texts}

Director Vane did not work in a dark room. His office on the 84th floor of the Zenith Spire was a temple of light—floor-to-ceiling glass that looked out over the grey, undulating carpet of the Seattle Fog. From here, the city looked like a circuit board, and Vane was the current that ensured every trace remained powered.

He wasn't looking at the view. He was looking at a single, microscopic red dot on his primary holographic array. 

\textit{Discrepancy: \$0.012,} the display whispered in a crisp, synthetic tone. 

To a human, twelve-tenths of a cent was a rounding error, a speck of dust in the wind of a trillion-dollar economy. To Vane, it was a puncture wound.

``Trace the origin,'' Vane said. His voice was like the city itself: calm, precise, and entirely devoid of friction.

\systemcall{SOURCE: SOUTH END LOGISTICS TERMINAL \\ ASSET: AIR FILTRATION UNIT [REF: 88-X] \\ STATUS: DISPOSED // REASON: OBSOLESCENCE \\ NOTE: TRANSACTION COMPLETED VIA STANDARDIZED EXTERNAL LEASE}

Vane leaned back in his chair, his fingers steepled. The South End terminal. It was a high-volume, low-priority node. It handled the ``Residuals'' — the items the market had decided were no longer worth the cost of storage. 

Normally, these items were sold to secondary recyclers or shipped to landfills. The money moved. The cycle closed. 

But this unit—Ref: 88-X—had been ``purchased" by an entity called the \textit{Common Fund}. 

Vane tapped a command, and the Fund’s registration data unfurled. It was a masterpiece of legal transparency. It had a tax ID. It had a registered agent. It paid its fees on time, in full, and in the correct currency. 



``So where is the leak?'' he murmured to himself.

He opened the secondary metabolism chart. Usually, when an entity buys a resource, they eventually sell it, or the labor used to maintain it generates a taxable service. But the Common Fund was a dead end. The resources went in, the money was paid, and then... nothing. No resale. No service contracts. No secondary market activity. 

The filter was gone. Not stolen, but \textbf{Internalized}. 

It was as if a part of the city’s physical body had simply stopped reporting to the brain. To Vane, this was more than a clerical error. It was \textbf{Economic Entropy}. 

``Identify the certifying officer for the 88-X disposal,'' Vane commanded.

\systemcall{OFFICER: ELARA [LOGISTICS-JUNIOR-04] \\ STATUS: ACTIVE // EFFICIENCY RATING: 94.2\% \\ RECENT ACTIVITY: TELEMETRY FAULT INVESTIGATION [SECTOR 7-B]}

Vane watched Elara’s file float in the air. A unremarkable face. A standard career trajectory. A variable that had always stayed within its expected range. 

But then he saw the ``Telemetry Fault'' in Sector 7-B. The same sector where the signals kept vanishing. The same sector where the Common Fund had its registered ``Warehouse.''

He didn't call the police. He didn't trigger an arrest warrant. In the Legacy system, you didn't kill an infection with a hammer; you starved it.

``Initiate a `Maintenance Lockout' for Sector 7-B,'' Vane said. ``Cite `Infrastructure Degradation.' Cut the grid-tie, disable the public transit nodes, and flag all `Common Fund' assets for a Mandatory Regulatory Audit. I want to see how long their `Internal Metabolism' lasts when the lungs of the city stop pumping.''

He looked back out at the Fog. Somewhere down there, a Junior Analyst was playing a game she didn't understand. She thought she was being clever by rerouting a few filters. She didn't realize that in Vane’s world, an error was a target.

``Let's see what you’re breathing now, Elara,'' he whispered.
